HL-LHC Computing Review:\\Common Tools and Community Software

### 2020-09-24 LHCC/2020/2020-01/ctcs.tex
First version of authors
Add author processing script (taken from CWP version)
Add initial (incomplete) list of some authors
Infrastructure and fixes
Add a Makefile that regenerates the document

Add a footnote hyperlink to mail the HSF editorial secretariat
Update LaTeX footnotes to symbols to avoid clashing with authors

Remove some spurious unicode (fi ligature) from generators text
Update DOI for CTCS Snowmass
Much more complete author list now

% HSF Document Number (only for arXiv)
\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-DOC-2020-01 \\
 & & 10.5281/zenodo.3779250 \\
 & & May 1, 2020 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{2.0cm}

@@

\author{High-Energy Physics Software Foundation}

>>>>

% HSF Document Number (only for arXiv)
\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-DOC-2020-01 \\
 & & 10.5281/zenodo.4009114 \\
 & & 31 August, 2020 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{2.0cm}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

@@

\author{HEP Software Foundation\footnote{\href{mailto:hsf-editorial-secretariat@googlegroups.com}{hsf-editorial-secretariat@googlegroups.com}}:
  \input{authors}
}
